---
date: "`r Sys.Date()`"
output: 
  html_document :
    theme : cerulean
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# *STEPHEN RENALDO SETIADI*

## **S4665076**

## ---------------------------------------------------------------------

# ASSESSMENT 2


```{r}
library(tidyverse)
library(tidymodels)
library(modeldata)
library(skimr)
library(kableExtra)
library(lubridate)
```


# Part 1: formatting RMarkdown document  (2 marks)

1. Create an Rmarkdown document with webpage as output (same as in setup)


At the start of the output document include your name in italic font and 
your student id in bold font as level 2 heading 

Separate with a solid line 

Include the title “Assignment 2” as level 1 heading 

Separate with a solid line 

List all tasks in the assignment as headings of the third level and include your results (=output) below each task showing your R code. 

https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-11-20

Tasks:

See the definition of variables in a separate section “Data dictionary”

To import the data use 

```{r}
thanks_meal <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv"
)
```

# Part 2: Data Wrangling and visualization 38 marks

For all tables below, you need to use the RMarkdown functionality to present tables (`kable`). 

### 1. Display the first 10 rows of the dataset using `kable()` function (1 marks). 

```{r}
kable(thanks_meal[1:10, ],)%>%
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


### 2. Using `skim()` display the summary of variables. 

Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type? 
Write 2-3 sentences with your explanation. (2 marks)

Answer: To predict a family income based on their menu we can use a variabel such as "Age variable", "gender variable" to create the analysis output of the family income/

Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type? (2 marks)

Answer: To predit a community type or Us_region we can we can use the variable "watch program variable" and "main_dish"
  

```{r}
skim(thanks_meal)
```


```{r}
sapply(thanks_meal, class)
```


### 3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).


```{r}
thanks_meal_parse<-thanks_meal %>%
  mutate(family_income = fct_relevel(fct_reorder(family_income, parse_number(age)),"Prefer not to answer"))
```
  
```{r}
skim(thanks_meal_parse)
```


### 4. What is the number of people who celebrate? (1 mark)
Answer : The number of people who celebrate is 980

```{r}
thanks_meal_parse%>%
count(celebrate, sort = TRUE, name = "People")%>%
  filter(celebrate!= "No")
```

### 5. What are categories and insights for each main dish served and the method it is prepared? (2 marks)


```{r}
thanks_meal_parse%>%
  count(main_dish, main_prep, sort = TRUE, name = "Total") %>%
  filter(main_dish!= "I don't know",main_dish!=  "Other (please specify)", main_prep!= "I don't know",main_prep!= "Other (please specify)")%>%
  drop_na(main_dish, main_prep)%>%
  kable("pipe")
```

### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
Write 2-3 sentences with your explanation of each insight. (4 marks)

```{r}
data_viz <- thanks_meal_parse%>%
  count(main_dish, main_prep, sort = TRUE, name = "Total") %>%
  filter(main_dish!= "I don't know",main_dish!=  "Other (please specify)", main_prep!= "I don't know",main_prep!= "Other (please specify)")%>%
  drop_na(main_dish, main_prep)
```

```{r}
data_viz$Total<-as.factor(data_viz$Total)
```

```{r}
data_viz %>%
  ggplot(aes(Total, main_dish,fill = main_prep))+
  geom_col()+
  theme_bw()+
  theme(legend.position="top")+
  theme(legend.background 
        = element_rect(fill="lightblue",size=0.5, 
                       linetype="solid", colour ="darkblue"))
  
```

```{r}
data_viz %>%
  ggplot(mapping = 
           aes(x = Total, y = main_dish , color = main_prep))+
  geom_point(size = 3, )+
  theme_linedraw()+
  theme(legend.position="top")+
  theme(legend.background 
        = element_rect(fill="lightblue",size=0.5, linetype="solid"))

```


```{r}
data_viz%>%
  ggplot(aes(main_dish,Total, color=main_prep, shape=main_prep))+
    geom_point()+
  theme(legend.position="bottom", legend.box = "horizontal")
  
```


### 7. How many use cranberry sauce? How many use gravy? 2marks

Cranbery Sauce = 803, and gravy = 892

```{r}
thanks_meal_parse%>%
  drop_na(cranberry, gravy)%>%
  count(cranberry, sort = TRUE)%>%
  filter(cranberry!= "None", cranberry!= "Other (please specify)")%>%
  kable("pipe")
```

```{r}
thanks_meal_parse%>%
  drop_na(cranberry, gravy)%>%
  count(gravy, sort = TRUE, name = "Sauce" )%>%
  filter(gravy!= "No")%>%
  kable("pipe")
```

### 8-9. What is the distribution of those who celebrate across income ranges. Create a data viz.Write 2-3 sentences with your explanation of each insight. (4 marks) 

The distribution across income range 

```{r}
income_range_viz <-thanks_meal_parse%>%
  count(family_income, celebrate, name = "Total", sort = TRUE)%>%
  filter(family_income!= "Prefer not to answer", celebrate!="No")
  
```

```{r}
print(income_range_viz)
```

There are 10 groups of family income distribution from the smallest range of 52 family with income $0-9,999, and 26 family with income range $175,000 to $199,000 which represent the smallest distribution of income range.

predominantly, there are 166 distribution family income with range $25,000 to $49,000. 


```{r}
income_range_viz %>%
  ggplot(aes(family_income, Total, fill = celebrate)) +
  geom_point(size =3, colour = "blue") +
  coord_flip()+
  labs(x = "Family Income", y = "Total number who Celebrate",
       title = "Distribution of those who celebrate")+
  theme_bw()
```


### 10. Use the following code to create a new data set 2 mark

select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))

Write 2-3 sentences with your explanation of what it does. (4 marks)

```{r}
thaks_meal_obs <- thanks_meal_parse%>%
select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
```


This function are generate a data trasnformation. This function manipulate variable to create a new data set  with combining all the variable that starts with  (id, 'side', 'pie' and 'dessert') 
``select(id, starts_with("side"),``
        ``starts_with("pie"),``
         ``starts_with("dessert"))``

removing variables  name side15, pie13 and dessert12

`select(-side15, -pie13, -dessert12)``

and also droping "NA" value, "None" value and other Other (please specify) from the selected function
``filter(!is.na(value)``
         ``!value %in% c("None", "Other (please specify)"))``

and create a new data frame with new length, size and observation value. with  ``gather(type, value, -id)`` 

create a new variable from type that only contain value
``mutate(type = str_remove(type, "\\d+"))``

### 11-12. Install package `widyr` and use `pairwise_cor()` function 

https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor

Write 2-3 sentences with your explanation of what it does. (2 marks)
Use this code for the new dataset
`
pairwise_cor(value, id, sort = TRUE)

```{r}
#install.packages("widyr")
```

This function call pearson's correlation to get the summary and descriptive statistic and test value of two different variable based on the variable that link them together to perform "Pairwise deletion" (the variable that link or the independent value is "id") Please see below example  


```{r}
library(widyr)
library(gapminder)
```

```{r}
thanks_meal %>%
  filter(!is.na(community_type), 
         family_income!= "Prefer not to answer")%>%
  pairwise_cor(age, family_income, id, sort = TRUE)
```

Write 1 sentence with your explanation of what insights it shows. (2 marks)

The correlations of pairs of items in a column age and family income based on id column, generate a corellation value  

### 13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset. 8 marks

```{r}
library(randomForest)
library(modeldata)
library(tidymodels)
library(skimr)
library(stats)
library(caret)
library(readxl)
```


```{r}
predict_model_data <- thanks_meal_parse %>%
  filter(family_income!= "Prefer not to answer",!is.na(age), !is.na(community_type), !is.na(watch_program),!is.na(us_region) )%>%
  select(id, family_income ,community_type, watch_program, age, us_region)
```


```{r}
skim(predict_model_data)
```


```{r}
predict_model_data$family_income <- droplevels(predict_model_data$family_income)
```


```{r}
predict.community.rf <- randomForest(family_income~ community_type, 
                           data = predict_model_data,
                           importance=TRUE, proximity=TRUE)
```


```{r}
print(predict.community.rf)
```


```{r}
predict.age.rf <- randomForest(family_income~ age, 
                           data = predict_model_data,
                           importance=TRUE, proximity=TRUE)
```

```{r}
print(predict.age.rf)
```

```{r}
predict.region.rf <- randomForest(family_income~ us_region, 
                           data = predict_model_data,
                           importance=TRUE, proximity=TRUE)
```

```{r}
print(predict.region.rf)
```
*Explain your choice of variables (3 sentences)* 
The age, US region and community type variable best to represent the family income as the three are explanatory variable 

*Write 2 sentences explaining which model os best.*
Random Forest is best to be used both as the data contain Continuous and Categorical Variable(dependent).


#### Resources:

RMarkdown tutorial https://rmarkdown.rstudio.com/lesson-1.html

ggplot2: Elegant Graphics for Data Analysis https://ggplot2-book.org/